Linear vertical shear instability in astrophysical disks: a semi-numerical study

### 2014-12-22 numerical.tex
corrected beta vs nz estimate, updated numerical adiabatic section
updated codes, added gloop and renamed var_kx to bloop. these codes loop over gmma or bcool
minor paper udpate

Note that the decay lengthscale is rougly the height within which
vertical shear is larger than the buoyancy frequency squared. That is,
\begin{align*}
\left|r\frac{d\Omega^2}{dz}\right|\gtrsim N_z^2
\end{align*}
for
\begin{align*}
  \left|\frac{z}{\epsilon r}\right| \lesssim \frac{\epsilon|q|\gamma}{\gamma-1},
\end{align*}
in a thin, vertically isothermal disk. This evaluates to $z\sim
0.2\epsilon r$ for the current disk model, consistent with
Fig. \ref{lowfreq_eigenfunc_adia}.

Furthermore, the growth rate to should be no larger than the
maximum vertical shear available within this decay lengthscale. Using 
Eq. \ref{max_growth} as a rough guide, 
\begin{align}
  \frac{\nu}{\epsilon\Omega_k}<\frac{\epsilon |q|^2}\gamma{2(\gamma-1)},
\end{align}
or $\nu< 0.1\epsilon\Omega_k$ is expected in our disk model,
consistent with numerical results.

@@

@@

\subsection{Vertically non-isothermal disks}
{\bf big gamma > 1, with tcool}

>>>>

Coincidentally, this decay lengthscale is rougly the height within which
vertical shear is larger than the buoyancy frequency squared. That is,
\begin{align*}
\left|r\frac{d\Omega^2}{dz}\right|\gtrsim N_z^2
\end{align*}
for
\begin{align*}
  \left|\frac{z}{\epsilon r}\right| \lesssim \frac{\epsilon|q|\gamma}{\gamma-1},
\end{align*}
in a thin, vertically isothermal disk. This evaluates to $z\sim
0.2\epsilon r$ for the current disk model, consistent with
Fig. \ref{lowfreq_eigenfunc_adia}.

Furthermore, the growth rate to should be no larger than the
maximum vertical shear available within this decay lengthscale. Using 
Eq. \ref{max_growth} as a rough guide, 
\begin{align}
  \frac{\nu}{\epsilon\Omega_k}<\frac{\epsilon |q|^2\gamma}{2(\gamma-1)},
\end{align}
or $\nu< 0.1\epsilon\Omega_k$ is expected in our disk model,
consistent with numerical results.

@@

\subsubsection{Other adiabatic indices}

@@

\subsection{Vertically non-isothermal disks}
{\bf big gamma larger than 1 but equal to small gamma, with tcool}

\subsection{Non-uniform thermal relaxation} 
{\bf variable tcool, large at midplane, small in atmosphere. simplest
  model is to multiply tcool by background density}
